\hspace{1cm} Do syntactic and semantic similarity lead to interference effects? \newline Evidence from self-paced reading and event-related potentials using German

### 2024-08-12 paper/main.tex
Updated via the Open Science Framework

\Copy{figpriorposteriordata}{
\begin{figure}[htpb]
    \caption{The prior predictions on the microvolt scale for syntactic and semantic interference and their interaction \textcolor{blue}{from three versions of the Lewis and Vasishth (2005) cue-based retrieval model.}
    %using the two cues \{$\pm$ subject-in-same-clause\} and \{$\pm$ animate\}. 
    The data with 95 \% credible intervals are shown in red.}\label{fig:model_predictions_ERP}
        \centering
         \includegraphics[width=\textwidth]{images/compmod_predictions.png}
\end{figure}
}

@@

%\textcolor{blue}{Using the above method, we estimate marginal likelihood for each candidate model under six different prior assumptions. The Bayes factor in favor of a model M$_1$ compared to a model M$_2$, i.e., BF$_{12}$, is computed as the ratio of the marginal likelihoods of M$_1$ and M$_2$. The Bayes factor BF$_{12}$ represents the extent to which the model M$_1$ is more likely than M$_2$ given the data. Following the convention from \textcite{jeffreys1998theory}, a Bayes factor above 10 is interpreted as strong evidence in favor of M$_1$ and a value between 3 and 10 is interpreted as moderate evidence in favor of M$_1$ (see also Table \ref{tab:bf_interpretation}).}

\textcolor{blue}{From the marginal likelihoods, we computed Bayes factors for the two-cues model compared to the three-cues model and the one-cue model. That is, the marginal likelihood of the two-cues model $\mathrm{M_1}$ was divided by the marginal likelihood of the three-cues model $\mathrm{M_2}$ and one-cue model $\mathrm{M_3}$ to obtain the Bayes factors $BF_{12}$ and $BF_{13}$, respectively. Following the convention from \textcite{jeffreys1998theory}, a Bayes factor above 10 is interpreted as strong evidence in favor of the two-cues model and a value between 3 and 10 is interpreted as moderate evidence in favor of the two-cues model compared to the competing model (see also Table \ref{tab:bf_interpretation}).}

>>>>

\Copy{fig:model_predictions_ERP}{
\begin{figure}[htpb]
    \caption{The prior predictions on the microvolt scale for syntactic and semantic interference and their interaction \textcolor{blue}{from three versions of the Lewis and Vasishth (2005) cue-based retrieval model.}
    %using the two cues \{$\pm$ subject-in-same-clause\} and \{$\pm$ animate\}. 
    The data with 95 \% credible intervals are shown in red.}\label{fig:model_predictions_ERP}
        \centering
         \includegraphics[width=\textwidth]{images/compmod_predictions.png}
\end{figure}
}

@@

\textcolor{blue}{From the marginal likelihoods, we computed Bayes factors for the two-cues model compared to the three-cues model and the one-cue model. That is, the marginal likelihood of the two-cues model $M_1$ was divided by the marginal likelihood of the three-cues model $M_2$ and one-cue model $M_3$ to obtain the Bayes factors $BF_{12}$ and $BF_{13}$, respectively. Following the convention from \textcite{jeffreys1998theory}, a Bayes factor above 10 is interpreted as strong evidence in favor of the two-cues model and a value between 3 and 10 is interpreted as moderate evidence in favor of the two-cues model compared to the competing model (see also Table \ref{tab:bf_interpretation}).}
